---
title: "RFDataset"
author: "Haoming"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
library(dplyr)
library(readxl)
library(stringr)
library(gmodels)
library(tidyr)

library(stats)
library(lme4)
library(lmtest)

library(scales)
library(tidyverse)
library(grid)


library(fastR2)
setwd("/Users/zhm/R/CoHOST")
```

## Read Index Data
```{r index, warning=FALSE}
ds <- read_xlsx("IndexRF_data_forHaoming.xlsx")
ds1 <- ds[,-c(16,17)]

names(ds1)<-str_replace_all(names(ds1), c(" " = "_", ":"=""))
ds2 <- rename(ds1,SubjectID=Subject_ID...1)

ds2 <- as.data.frame(ds2)
ds3 <- ds2[!ds2$infected_household=="excluded",]
sum(ds3$infected_household==0)

ds3$household_infected_at_baseline[ds3$household_with_new_secondary_case==1]=2
ds3$Ethnicity[ds3$SubjectID=="UNC-COV073"]="Hispanic or Latino"

ds3$infected_household[ds3$infected_household==0]=2
ds3$boxcolumn <- ifelse(ds3$infected_household==2,"No secondary cases",ifelse(ds3$household_infected_at_baseline==1,"Infected cases at baseline","New secondary cases"))

ds3$infectedbi <- factor(ds3$infected_household,levels = 1:2,labels = c("event","noevent"))
ds3$infectedbi <- relevel(ds3$infectedbi,"noevent")
```

```{r merge}
getwd()
ds9 <- read.csv("IndexRF_data_2.csv",sep = ',', stringsAsFactors = FALSE)
ds8 <- rename(ds9,SubjectID=Subject.ID.)
ds8$Arm2=rep(0,200)
ds8$Arm2[ds8$Event.Name=="Day 1 (Arm 2: COVID-HC Arm)"]=1
ds8$Event.Name[ds8$Event.Name=="Day 1 (Arm 2: COVID-HC Arm)"]="Day 1 (Arm 1: COVID Arm)"
ds8$Event.Name[ds8$Event.Name=="Day 28 (Arm 2: COVID-HC Arm)"]="Day 28 (Arm 1: COVID Arm)"
ds8$ELISA..IgG..Reading.[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
ds8$ELISA..IgG..Reading.[ds8$Event.Name=="Day 28 (Arm 1: COVID Arm)"]
ds8$IgG.band.[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
ds8$IgG.band.[ds8$Event.Name=="Day 28 (Arm 1: COVID Arm)"]
ds8$Symptom.Duration.[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
ds8$Symptom.Duration.[ds8$Event.Name=="Day 28 (Arm 1: COVID Arm)"]
ds8$Rapid.Antibody.Test.Results.[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
ds8$Rapid.Antibody.Test.Results.[ds8$Event.Name=="Day 28 (Arm 1: COVID Arm)"]
# ds8$ELISA..IgG..Reading.[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
# ds8$ELISA..IgG..Reading.[ds8$Event.Name=="Day 28 (Arm 1: COVID Arm)"]
# ds8$IgG.band.[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
# ds8$IgG.band.[ds8$Event.Name=="Day 28 (Arm 1: COVID Arm)"]


ds7 <- ds8[ds8$Event.Name=="Day 1 (Arm 1: COVID Arm)",]
ds7$BMI[ds7$Arm2==1]=ds7$BMI.1[ds7$Arm2==1]
ds7$Diabetes[ds7$Arm2==1]=ds7$Diabetes.1[ds7$Arm2==1]
ds7$Highest.education.level..select.one..[ds7$Arm2==1]=ds7$Highest.education.level..select.one...1[ds7$Arm2==1]
ds7$Occupation..please.be.as.specific.as.possible..[ds7$Arm2==1]=ds7$Occupation..please.be.as.specific.as.possible...1[ds7$Arm2==1]

ds7 <- select(ds7,-c(9:12))
ds6 <- merge(x = ds3, y = ds7, by = "SubjectID", all.x = TRUE)

ds6[ds6==""] <- NA
```

## read HC data 
```{r HCsdata}
ds11 <- read_xlsx("HCsRF_data.xlsx")
names(ds11)<-str_replace_all(names(ds11), c(" " = ".", ":"=""))
ds11$Arm2=rep(0,364)
ds11$Arm2[ds11$Event.Name=="Day 1 (Arm 2: COVID-HC Arm)"]=1
ds11$Event.Name[ds11$Event.Name=="Day 1 (Arm 2: COVID-HC Arm)"]="Day 1 (Arm 1: COVID Arm)"
ds11$Event.Name[ds11$Event.Name=="Day 0 (Arm 2: COVID-HC Arm)"]="Day 0 (Arm 1: COVID Arm)"
ds11$Race[ds11$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
ds11$Race[ds11$Event.Name=="Day 0 (Arm 1: COVID Arm)"]
ds11$Ethnicity[ds11$Event.Name=="Day 1 (Arm 1: COVID Arm)"]=
ds11$Ethnicity[ds11$Event.Name=="Day 0 (Arm 1: COVID Arm)"]
ds12 <- ds11[ds11$Event.Name=="Day 1 (Arm 1: COVID Arm)",]
ds12 <- ds12 %>%
    rename(SubjectID=Subject.ID) %>%
    mutate(infected_household=ifelse(ds12$`Is.this.subject..considered.a.secondary.case.that.was.infected.at.baseline?`=="Yes"|ds12$`Does.this.subject.represent.a.NEW.secondary.case.based.on.PCR.or.Ab.testing?`=="Yes",1,2)) %>% 
    mutate(household_infected_at_baseline=ifelse(ds12$`Is.this.subject..considered.a.secondary.case.that.was.infected.at.baseline?`=="Yes",1,ifelse(ds12$`Does.this.subject.represent.a.NEW.secondary.case.based.on.PCR.or.Ab.testing?`=="Yes",2,NA)))

ds12$household <- substring(ds12$SubjectID,regexpr("V",ds12$SubjectID)+1,10)

ds12$dropout <- ifelse(ds12$SubjectID=="UNC-COV007-001"|ds12$SubjectID=="UNC-COV007-004"|ds12$SubjectID=="UNC-COV007-007"|ds12$SubjectID=="UNC-COV020-004"|ds12$SubjectID=="UNC-COV039-001"|ds12$SubjectID=="UNC-COV045-002",1,0)

ds12 <- filter(ds12,dropout==0)
ds12$infectedbi <- factor(ds12$infected_household,levels = 1:2,labels = c("event","noevent"))
ds12$infectedbi <- relevel(ds12$infectedbi,"noevent")
table(ds12$infectedbi)
# table(ds12$Race,ds12$household_infected_at_baseline)
# table(ds12$Ethnicity, ds12$infected_household)
# 
# ds12$Race[ds12$Ethnicity=="Hispanic or Latino"]="Hispanic or Latino"
# 
# ds12$racebi182 <- ifelse(ds12$Race=="White or Caucasian",1,ifelse(ds12$Race=="Unknown",NA,0))
# table(ds12$racebi182,ds12$household_infected_at_baseline)
# mrace182 <- glmer(infectedbi ~ racebi182 + (1|household), data = ds12, family = "binomial")
# coef(summary(mrace182))
# ds12$household

# ?wilson.ci
# wilson.ci(56,79,conf.level = 0.95)
```

## Total data
```{r}
ds6$household <- substring(ds6$SubjectID,regexpr("V",ds6$SubjectID)+1,10)
ds6$household
ds30left <- select(ds6,SubjectID,household,"reported_number"=How.many.people.are.in.your.household.live.with.you..including.yourself..) 
ds30right <- select(ds12,SubjectID,household)
ds30right <- ds30right %>% mutate("reported_number"=NA)

ds30 <- rbind(ds30left,ds30right)


ds30 <- ds30 %>% 
  group_by(household) %>% 
  mutate(n=n())
sum(ds30$reported_number==ds30$n,na.rm = T)
53/92
# ds30 <- ds30 %>% 
#   group_by(household) %>% 
#   mutate(new=reported_number[which(!is.na(reported_number))])


ds12 %>% 
    group_by(household) %>% 
  mutate(n=n())
```



## Index Age
```{r Index Age}
ds3$Agecat <- cut(ds3$Age,c(0,17,50,120))

CrossTable(ds3$Agecat,ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$Agecat,ds3$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)


ds3$agebi1=ifelse(ds3$Age<18,1,0)
ds3$agebi2=ifelse(18<=ds3$Age&ds3$Age<=50,1,0)
ds3$agebi3=ifelse(ds3$Age>50,1,0)

miage <- glm(infectedbi ~ agebi3, data = ds3, family = binomial)
coef(summary(miage))
```

## Index Sex
```{r Index Sex}
CrossTable(ds3$Sex,ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$Sex,ds3$household_infected_at_baseline,prop.t = F,prop.r = F,prop.chisq = F)

ds3$Sex
misex <- glm(infectedbi ~ Sex, data = ds3, family = binomial)
coef(summary(misex))
```
## Index Mask_wearing
```{r Index Mask_wearing}
CrossTable(ds3$mask_inside_home, ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$mask_inside_home, ds3$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)

mihomemask <- glm(infectedbi ~ mask_inside_home, data = ds3, family = binomial)
coef(summary(mihomemask))
```

## Index Race/ethnicity
```{r Index Race/ethnicity}
ds3$Race[ds3$Ethnicity=="Hispanic or Latino"] <- ds3$Ethnicity[ds3$Ethnicity=="Hispanic or Latino"]

CrossTable(ds3$Race, ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$Race, ds3$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)
CrossTable(ds3$Ethnicity, ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$Ethnicity, ds3$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)


ds3$whitebi=ifelse(ds3$Race=="White or Caucasian",1,0)
ds3$blackbi=ifelse(ds3$Race=="Black or African American",1,0)
ds3$latinobi=ifelse(ds3$Ethnicity=="Hispanic or Latino",1,0)
ds3$otherracebi=ifelse(ds3$Race!="White or Caucasian"&ds3$Race!="Black or African American"&ds3$Race!="Hispanic or Latino",1,0)

mirace <- glm(infectedbi ~ latinobi, data = ds3, family = binomial)
coef(summary(mirace))
```

## Index Viral_load
```{r Index Viral_load}
ds3$NPcat <- cut(ds3$D1_NP,c(-1,1000000,1000000000),labels = c(0,1))

CrossTable(ds3$NPcat, ds3$infected_household,prop.t = F,prop.chisq = F,fisher = T)
CrossTable(ds3$NPcat, ds3$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)

mivl <- glm(infectedbi ~ NPcat, data = ds3, family = "binomial")
coef(summary(mivl))
exp(0.63908+1.96*0.5760825)


median(ds3$D1_NP[ds3$household_infected_at_baseline==1],na.rm = T)
median(ds3$D1_NP[ds3$household_infected_at_baseline==2],na.rm = T)
median(ds3$D1_NP[ds3$infected_household==1],na.rm = T)
median(ds3$D1_NP[ds3$infected_household==2],na.rm = T)

log10(median(ds3$D1_NP[ds3$household_infected_at_baseline==2],na.rm = T))/log10(median(ds3$D1_NP[ds3$infected_household==2],na.rm = T))
# ds4 <- ds3[!(ds3$Rapid_Antibody_Test_Results=="Positive"),]
# ds4$NPcat <- cut(ds4$D1_NP,c(-1,1000000,1000000000),labels = c(0,1))
# 
# CrossTable(ds4$NPcat, ds4$infected_household,prop.t = F,prop.chisq = F)
# CrossTable(ds4$NPcat, ds4$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)

ds6$NPcat <- cut(ds6$D1_NP,c(-1,1000000,1000000000),labels = c(0,1))
ExcludeD1Ab_ds6 <- filter(ds6,ds6$ELISA..IgG..Reading.=="Equivocal"|ds6$ELISA..IgG..Reading.=="Negative"|(is.na(ds6$ELISA..IgG..Reading.)&is.na(ds6$IgG.band.)))


CrossTable(ExcludeD1Ab_ds6$NPcat, ExcludeD1Ab_ds6$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ExcludeD1Ab_ds6$NPcat, ExcludeD1Ab_ds6$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)

# ExcludeD1Ab_ds6[ExcludeD1Ab_ds6$infected_household==0&!is.na(ExcludeD1Ab_ds6$D1_NP),]


ds3$D7_NMTcat=cut(ds3$D7_NMT,c(-1,9,100000000))
CrossTable(ds3$D7_NMTcat, ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$D7_NMTcat, ds3$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)


ds6$Abpositive = ifelse(is.na(ds6$ELISA..IgG..Reading.)&is.na(ds6$IgG.band.),0,ifelse(ds6$ELISA..IgG..Reading.=="Positive"|(is.na(ds6$ELISA..IgG..Reading.)&!is.na(ds6$IgG.band.)),1,0))

dstest <- select(ds6,ELISA..IgG..Reading.,IgG.band.,Abpositive)
table(ds6$Abpositive)

dsbasevsun<- filter(ds6,ds6$household_infected_at_baseline!=2|is.na(ds6$household_infected_at_baseline))
dsbasevsun$household_infected_at_baseline[is.na(dsbasevsun$household_infected_at_baseline)]=0
dsbasevsun$household_infected_at_baseline
miabpositive<- glm(household_infected_at_baseline ~ Abpositive, data=dsbasevsun, family = "binomial" )
coef(summary(miabpositive))
table(dsbasevsun$Abpositive,dsbasevsun$household_infected_at_baseline)
```

## ggplot
```{r plot}
# + coord_cartesian(ylim = c(0,1e8))
ds6$Abpositive = ifelse(is.na(ds6$ELISA..IgG..Reading.)&is.na(ds6$IgG.band.),2,ifelse(ds6$ELISA..IgG..Reading.=="Positive"|(is.na(ds6$ELISA..IgG..Reading.)&!is.na(ds6$IgG.band.)),1,2))

dstest <- select(ds6,ELISA..IgG..Reading.,IgG.band.,ExcludeAb)
table(ds6$Abpositive)


ds21 <- ds6[which(ds6$Abpositive==2),]
ds21$Abpositive = replicate(length(ds21$Abpositive),1)

ds22 <- rbind(ds21,ds6)
table(ds22$Abpositive)

options(scipen=2)

fci <- function(x) {
  ans <- boxplot.stats(x)
  data.frame(ymin = ans$conf[1], ymax = ans$conf[2], y = ans$stats[3])
}

exp_bold <- function(x) {
  lab <- lapply(x, function(x) log10(x))
  
  ans <- do.call(
    expression,
   lapply(paste(lab), function(x) bquote(bold("10"^.(x))))
  )
  for( i in (1:length(ans))){ 
         if(i%%2==1) ans[i] = ""
  }
  ans
}

 ggplot(data=ds22,aes(x=boxcolumn,y=D1_NP,fill=factor(Abpositive))) + 
  geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.8) + 
  xlab("Households") + ylab("Index NP viral load at baseline (copies/ul)") + 
  theme_classic()+ggtitle("") +
  scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
  scale_y_log10( breaks = trans_breaks("log10", function(x) 10^x)) 
 
 ggplot(data=ds22,aes(x=boxcolumn,y=D1_NP,fill=factor(Abpositive))) + 
  geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.8) + 
  xlab("Households") + ylab("Index NP viral load at baseline (copies/ul)") + 
  theme_classic()+ggtitle("") +
  scale_fill_manual(name = "", labels = c("Including Ab+", "Excluding Ab+"),values = c("white","gray"))+
  scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
  scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x,n=10),
              labels = function(x) exp_bold(x),limits = c(1,1e9)) +
  stat_summary(width=0.8,aes(x=boxcolumn,y=D1_NP,group=factor(Abpositive)), fun.data = fci, geom = "crossbar", 
    color="skyblue", fill= "lightblue",alpha = 0.5,position = position_dodge(width = .8)) +
   
  theme( plot.title = element_text(face="bold",size =14,vjust = 2),
        axis.text.x = element_text(face="bold", color="#000000", 
                           size=12, angle=0, vjust= 1),
        axis.title.y = element_text(face="bold",size =14,vjust=5),
        axis.title.x = element_text(face="bold",size =15,vjust = 0),
          axis.text.y = element_text(face="bold", color="#000000", 
                           size=14, angle=0,hjust=-0.3),
    axis.ticks.length.y = unit(.25, "cm"),
    axis.ticks.length.x = unit(.25, "cm"),
    legend.title = element_blank(),
    legend.text = element_text(face="bold",size =12),
    legend.key = element_rect(colour = "transparent", fill = "transparent"),
    legend.position = c(0.8, 0.1),
      plot.margin = margin(0.2, 0.2, 0.2, 0.5, "cm")
      ) +
  geom_jitter(data= subset(ds22,D1_NP>0),aes(boxcolumn,D1_NP),shape=16, position=position_dodge(width = 0.8))


?trans_breaks
# ggplot(data=ds22,aes(x=boxcolumn,y=D1_NP)) +
#   geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.8) +
#   xlab("Households") + ylab("Index NP Viral Load at Baseline (copies/ul)") +
#   theme_classic()+ggtitle("") +
#   scale_fill_manual(name = "", labels = c("Excluding Ab+", "Not Excluding Ab+"),values = c("darkgray","lightgray"))+
#   scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
#   scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x,n=9),
#               labels = function(x) exp_bold(x),limits = c(1,1e8)) +
#   stat_summary(width=0.8,aes(x=boxcolumn,y=D1_NP,fill=factor(ExcludeAb)), fun.data = fci, geom = "crossbar",
#     color = "skyblue", fill= "lightblue",alpha = 0.5,position = position_dodge(width = .8)) +
#   theme( plot.title = element_text(face="bold",size =14,vjust = 2),
#         axis.text.x = element_text(face="bold", color="#000000",
#                            size=8, angle=0, vjust= 1),
#         axis.title.y = element_text(face="bold",size =14),
#         axis.title.x = element_text(face="bold",size =14,vjust = -1),
#           axis.text.y = element_text(face="bold", color="#000000",
#                            size=12, angle=0),
#     axis.ticks.length.y = unit(.25, "cm"),
#     axis.ticks.length.x = unit(.25, "cm"),
#     legend.title = element_blank(),
#     legend.text = element_text(face="bold",size =10),
#     legend.key = element_rect(colour = "transparent", fill = "transparent"),
#     legend.position = c(0.8, 0.1)) +
# 
#   geom_jitter(data= subset(ds22,D1_NP>0),aes(boxcolumn,D1_NP),shape=16, position=position_dodge(width = 0.8)) +
#   facet_wrap(~ExcludeAb)

# box1 <- ggplot(data=ds3) + 
#   geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.8) + 
#   xlab("Infection Status") + ylab("NP Viral Load at Baseline (copies/ul)") + 
#   theme_classic()+ggtitle("Index NP Viral Load at Baseline") + 
#   scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
#   scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x),
#               labels =exp_bold) +
#   stat_summary(aes(x=boxcolumn,y=D1_NP), fun.data = fci, geom = "crossbar", 
#     colour = NA, fill = "skyblue", width = 0.8, alpha = 0.5) +
#   
#   theme( plot.title = element_text(face="bold",size =14,vjust = 2),
#         axis.text.x = element_text(face="bold", color="#000000", 
#                            size=12, angle=0, vjust= -2),
#         axis.title.y = element_text(face="bold",size =14),
#           axis.text.y = element_text(face="bold", color="#000000", 
#                            size=12, angle=0),
#     axis.ticks.length.y = unit(.25, "cm"),
#     axis.ticks.length.x = unit(.25, "cm")) +
#   xlab("") +
#   geom_jitter(aes(boxcolumn,D1_NP),shape=16, position=position_jitter(0.1))
# 
# 
# violin1 <- ggplot(data=ds3, aes(x=boxcolumn,y=D1_NP,fill=boxcolumn)) + 
#   geom_violin(aes(x=boxcolumn,y=D1_NP),alpha=0.4) +
#   geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.3,alpha=0.3) + 
#   xlab("Infection Status") + ylab("NP Viral Load at Baseline (copies/ul)") + 
#   theme_classic()+ggtitle("Index NP Viral Load at Baseline") + 
#   scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
#   scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x),
#               labels =exp_bold) +
#   stat_summary(aes(x=boxcolumn,y=D1_NP), fun.data = fci, geom = "crossbar", 
#     colour = NA, fill = "skyblue", width = 0.3, alpha = 0.8) +
#   
#   theme( plot.title = element_text(face="bold",size =14,vjust = 2),
#         axis.text.x = element_text(face="bold", color="#000000", 
#                            size=12, angle=0, vjust= -2),
#         axis.title.y = element_text(face="bold",size =14),
#           axis.text.y = element_text(face="bold", color="#000000", 
#                            size=12, angle=0),
#     axis.ticks.length.y = unit(.25, "cm"),
#     axis.ticks.length.x = unit(.25, "cm"),
#     legend.position = "none") +
#   xlab("") +
#   geom_jitter(aes(boxcolumn,D1_NP),shape=16, position=position_jitter(0.1)) +
#   scale_fill_grey()
# violin1
# 
# g1 <- ggplotGrob(box1)
# g2 <- ggplotGrob(violin1)
# g3 <- cbind(g1, g2, size = "first")
# grid.newpage()
#   grid.draw(g3)
# 
# # coord_trans()
# 
# box2 <- ggplot(data=ExcludeD1Ab_ds6) + 
#   geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.8) + 
#   xlab("Infection Status") + ylab("NP Viral Load at Baseline (copies/ul)") + 
#   theme_classic()+ggtitle("Index NP Viral Load at Baseline") + 
#   scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
#   scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x),
#               labels =exp_bold) +
#   stat_summary(aes(x=boxcolumn,y=D1_NP), fun.data = fci, geom = "crossbar", 
#     colour = NA, fill = "skyblue", width = 0.8, alpha = 0.5) +
#   
#   theme( plot.title = element_text(face="bold",size =14,vjust = 2),
#         axis.text.x = element_text(face="bold", color="#000000", 
#                            size=12, angle=0, vjust= -2),
#         axis.title.y = element_text(face="bold",size =14),
#           axis.text.y = element_text(face="bold", color="#000000", 
#                            size=12, angle=0),
#     axis.ticks.length.y = unit(.25, "cm"),
#     axis.ticks.length.x = unit(.25, "cm")) +
#   xlab("") +
#   geom_jitter(aes(boxcolumn,D1_NP),shape=16, position=position_jitter(0.1))
# box2
# 
# violin2 <- ggplot(data=ExcludeD1Ab_ds6, aes(x=boxcolumn,y=D1_NP,fill=boxcolumn)) + 
#   geom_violin(aes(x=boxcolumn,y=D1_NP),alpha=0.4) +
#   geom_boxplot(aes(x=boxcolumn,y=D1_NP), width=0.3,alpha=0.3) + 
#   xlab("Infection Status") + ylab("NP Viral Load at Baseline (copies/ul)") + 
#   theme_classic()+ggtitle("Index NP Viral Load at Baseline") + 
#   scale_x_discrete( labels=function(x) str_wrap(x, width=15) )+
#   scale_y_continuous(trans = log10_trans(), breaks = trans_breaks("log10", function(x) 10^x),
#               labels =exp_bold) +
#   stat_summary(aes(x=boxcolumn,y=D1_NP), fun.data = fci, geom = "crossbar", 
#     colour = NA, fill = "skyblue", width = 0.3, alpha = 0.8) +
#   
#   theme( plot.title = element_text(face="bold",size =14,vjust = 2),
#         axis.text.x = element_text(face="bold", color="#000000", 
#                            size=12, angle=0, vjust= -2),
#         axis.title.y = element_text(face="bold",size =14),
#           axis.text.y = element_text(face="bold", color="#000000", 
#                            size=12, angle=0),
#     axis.ticks.length.y = unit(.25, "cm"),
#     axis.ticks.length.x = unit(.25, "cm"),
#     legend.position = "none") +
#   xlab("") +
#   geom_jitter(aes(boxcolumn,D1_NP),shape=16, position=position_jitter(0.1)) +
#   scale_fill_grey()
# violin2
# g4 <- ggplotGrob(box2)
# g5 <- ggplotGrob(violin2)
# g6 <- cbind(g4, g5, size = "first")
# grid.newpage()
#   grid.draw(g6)
  

```
## Index Symptom_Severity
```{r Index Symptom_severity}

CrossTable(ds3$sx_severity, ds3$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds3$sx_severity, ds3$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)

ds3$mildbi <- ifelse(ds3$sx_severity==2,1,0)
ds3$modsevbi <- ifelse(ds3$sx_severity==11,1,0)
ds3$hospitalbi <- ifelse(ds3$sx_severity==12,1,0)

miseverity <- glm(infectedbi ~ hospitalbi, data = ds3, family = binomial)
coef(summary(miseverity))
```



## Index Comorbidities Education Healthcare_worker
```{r Index Comorbidities}
CrossTable(ds6$Diabetes, ds6$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds6$Diabetes, ds6$household_infected_at_baseline, prop.t = F,prop.r = F,prop.chisq = F)

midiabetes <- glm(infectedbi ~ Diabetes, data = ds6, family = binomial)
coef(summary(midiabetes))

ds6$BMIcat=cut(ds6$BMI,c(0,29.5,100))
CrossTable(ds6$BMIcat, ds6$infected_household,prop.t = F,prop.chisq = F)

miobesity <- glm(infectedbi ~ BMIcat, data = ds6, family = binomial)
coef(summary(miobesity))

CrossTable(ds6$Highest.education.level..select.one.., ds6$infected_household,prop.t = F,prop.chisq = F)
table(ds6$Highest.education.level..select.one..)
ds6$edubi1 <- ifelse(ds6$Highest.education.level..select.one..=="High school or lower", 1,0)
ds6$edubi2 <- ifelse(ds6$Highest.education.level..select.one..=="College degree", 1,0)
ds6$edubi3 <- ifelse(ds6$Highest.education.level..select.one..=="Graduate degree", 1,0)

miedu <- glm(infectedbi ~ edubi3, data = ds6, family = binomial)
coef(summary(miedu))

ds10 <- select(ds6,SubjectID,Occupation..please.be.as.specific.as.possible..,infectedbi)

ds10$healthcareworker[ds10$SubjectID=="UNC-COV092"] = 1
table(ds10$healthcareworker,ds10$infectedbi)
ds10$healthcareworker[is.na(ds10$healthcareworker)] = 0
mihealthcare <- glm(infectedbi ~ healthcareworker, data = ds10, family= "binomial")
coef(summary(mihealthcare))
```

## Index igG
```{r Index igG}



dsigg <- ds6 %>% 
    mutate(igg = ifelse((ELISA..IgG..Reading.=="Positive")|(is.na(ELISA..IgG..Reading.)&!is.na(IgG.band.)),"Positive",NA))
table(dsigg$igg)
dsigg$igg[dsigg$ELISA..IgG..Reading.=="Negative"|is.na(dsigg$ELISA..IgG..Reading.)&is.na(dsigg$IgG.band.)&(dsigg$Rapid_Antibody_Test_Results!="Rapid Ab Test Not Taken")]="Negative"
dsigg$igg[dsigg$ELISA..IgG..Reading.=="Equivocal"]="Equivocal"
CrossTable(dsigg$igg, dsigg$infected_household,prop.t = F,prop.chisq = F)

dsigg$pbi <- ifelse(dsigg$igg=="Positive",1,0)
dsigg$nbi <- ifelse(dsigg$igg=="Negative",1,0)
miigg <- glm( infectedbi ~ nbi, data=dsigg, family = "binomial")
coef(summary(miigg))

```

## Index Duration
```{r Index Duration}
CrossTable(ds6$Symptom.Duration.,ds6$infected_household,prop.t=F,prop.chisq=F)
quantile(ds6$Symptom.Duration.[ds6$infected_household==1],na.rm = T)

ds6$Symptom.Duration.[ds6$infected_household==1]
```

## Household Table
```{r Household Table}
mean(ds6$How.many.people.are.in.your.household.live.with.you..including.yourself..)
t.test(ds6$How.many.people.are.in.your.household.live.with.you..including.yourself..[ds6$infected_household==1], ds6$How.many.people.are.in.your.household.live.with.you..including.yourself..[ds6$infected_household==2],
       alternative = "two.sided",
       mu = 0, paired = FALSE, var.equal = FALSE,
       conf.level = 0.95,)

CrossTable(ds6$Approximately.how.many.square.feet.is.your.home..living.space..,ds6$infected_household,prop.t=F,prop.chisq=F)

ds6$spacecat=ifelse(ds6$Approximately.how.many.square.feet.is.your.home..living.space..==">2000 sq feet (>186 sq m)", ">2000",ifelse(ds6$Approximately.how.many.square.feet.is.your.home..living.space..=="Not sure",NA,"<2000"))
table(ds6$spacecat)

mispace <- glm( infectedbi ~ spacecat, data=ds6, family = "binomial")
coef(summary(mispace))

CrossTable(ds6$How.many.rooms.does.your.household.occupy..include.bedrooms..kitchen..common.rooms..but.not.bathrooms.or.garage..,ds6$infected_household,prop.t=F,prop.chisq=F, fisher = T)

miroomnumber <- glm( infectedbi ~ How.many.rooms.does.your.household.occupy..include.bedrooms..kitchen..common.rooms..but.not.bathrooms.or.garage.., data=ds6, family = "binomial")
coef(summary(miroomnumber))

mi0 <- glm (infectedbi ~ 1 , data=ds6, family = "binomial")
coef(summary(mi0))

lrtest(miroomnumber,mi0)

ds6$density=ifelse(ds6$How.many.rooms.does.your.household.occupy..include.bedrooms..kitchen..common.rooms..but.not.bathrooms.or.garage..!="6 or more rooms"&ds6$How.many.people.are.in.your.household.live.with.you..including.yourself..>3,1,0)


CrossTable(ds6$density,ds6$infectedbi,prop.t=F,prop.chisq=F, fisher = T)
20/22
wilson.ci(20,22,conf.level = 0.95)
midensity <- glm (infectedbi ~ density , data=ds6, family = "binomial")
coef(summary(midensity))
exp(1.7765)

CrossTable(ds6$Household.type.,ds6$infected_household,prop.t=F,prop.chisq=F)

ds6$Household.type.[ds6$Household.type.=="Other"] <- NA
ds6$Household.type.bi1=ifelse(ds6$Household.type.=="Apartment occupied by renter",1,0)
ds6$Household.type.bi2=ifelse(ds6$Household.type.=="Single-family home or townhome occupied by owner",1,0)
ds6$Household.type.bi3=ifelse(ds6$Household.type.=="Single-family home or townhome occupied by renter",1,0)

miownership <- glm (infectedbi ~ Household.type.bi3 , data=ds6, family = "binomial")
coef(summary(miownership))




```

## Race*density
```{r Race*density}
ds31 <- ds6
ds31$Race[ds31$Ethnicity=="Hispanic or Latino"]=ds31$Ethnicity[ds31$Ethnicity=="Hispanic or Latino"]
table(ds31$Race,ds31$density)
table(ds6$Race)


```

## P value
```{r Fishers Exact Test}
x=5
y=8
a <- matrix(c(x,y,64-x,28-y),nrow = 2)
fisher.test(a)


library(vcdExtra)
Input =(
"Infected       Yes        No
Hours
le3         11          2
4-6         14          15
gt6         71          45
")

Tabla = as.table(read.ftable(textConnection(Input)))


Tabla
sum (Tabla)

prop.table(Tabla,
           margin = NULL)


CMHtest(Tabla, strata = NULL, 
   rscores = "midrank", cscores = "midrank", 
   types = c("cor", "rmeans", "cmeans", "general"), 
   overall=FALSE)
```





##################################################################################################
                                            HC Data
##################################################################################################
  



## HC Relationship
```{r HC Relationship}
CrossTable(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

CrossTable(ds12$`Are.you.acting.as.a.primary.caregiver.to.the.COV-positive.person?`,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`Are.you.acting.as.a.primary.caregiver.to.the.COV-positive.person?`,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

```


## HC Age
```{r HC Age}
ds12$Agecat <- cut(ds12$Age,c(0,10,17,50,120))

CrossTable(ds12$Agecat,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$Agecat,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)
```


## HC Sex
```{r HC Sex}
CrossTable(ds12$Sex,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$Sex,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)
```



## HC Shared activities prior to enrollment
```{r HC Shared activities prior to enrollment}
names(ds12)[15:27] <- names(ds12)[15:27] %>% 
  substring(regexpr("=",names(ds12)[15:27])+1) %>% 
  str_replace_all(c("\\)"=" ","\\("=" "))

CrossTable(ds12$`Same.bed.for.sleeping `,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`Same.bed.for.sleeping `,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

CrossTable(ds12$`Same.room.for.sleeping `,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`Same.room.for.sleeping `,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

ds12 <- ds12 %>% mutate(Same.bathroom=(ds12$`Same.bedroom.bathroom `=="Checked"|ds12$`Same.general.bathroom `=="Checked"))
CrossTable(ds12$Same.bathroom,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$Same.bathroom,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

CrossTable(ds12$`Meals.eaten.together.at.the.dinner.table `,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`Meals.eaten.together.at.the.dinner.table `,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

CrossTable(ds12$`Shared.car.rides `,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`Shared.car.rides `,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

```

## HC Mask wearing
```{r HC Mask_wearing}
# ds12$Mask_how_often=ifelse(ds12$`How.often.do.you.wear.the.mask?.(check.all.that.apply).(choice=Most.of.the.day)`=="Checked"|ds12$`When.do.you.wear.the.mask?.(check.all.that.apply).(choice=Most.of.the.day)`=="Checked","Most_of_the_day",
#     ifelse(ds12$`How.often.do.you.wear.the.mask?.(check.all.that.apply).(choice=Sometimes)`=="Checked"|ds12$`When.do.you.wear.the.mask?.(check.all.that.apply).(choice=Sometimes)`=="Checked","Sometimes",
#     ifelse(ds12$`How.often.do.you.wear.the.mask?.(check.all.that.apply).(choice=Rarely)`=="Checked"|ds12$`When.do.you.wear.the.mask?.(check.all.that.apply).(choice=Rarely)`=="Checked","Rarely",NA)))
# CrossTable(ds12$Mask_how_often,ds12$infected_household,prop.t = F,prop.chisq = F)
# CrossTable(ds12$Mask_how_often,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)


ds12$Mask_at_home=ifelse(ds12$`When.do.you.wear.the.mask?.(check.all.that.apply).(choice=Inside.my.home)`=="Checked"|ds12$`Where.do.you.wear.the.mask?.(check.all.that.apply).(choice=Inside.my.home)`=="Checked","Yes","No")

ds12$Mask_at_home=ifelse(ds12[8]=="Unchecked"&ds12[9]=="Unchecked"&ds12[10]=="Unchecked"&ds12[31]=="Unchecked"&ds12[32]=="Unchecked"&ds12[33]=="Unchecked",NA,ds12$Mask_at_home)

CrossTable(ds12$Mask_at_home,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$Mask_at_home,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)


CrossTable(ds12$`Has.the.COVID.positive.contact.in.your.household.been.wearing.a.mask.in.the.past.week?`,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$`Has.the.COVID.positive.contact.in.your.household.been.wearing.a.mask.in.the.past.week?`,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)
```


## HC Ethnicity
```{r HC Ethnicity}
ds12$Race[ds12$Ethnicity=="Hispanic or Latino"] <- ds12$Ethnicity[ds12$Ethnicity=="Hispanic or Latino"]

CrossTable(ds12$Race,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$Race,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

CrossTable(ds12$Ethnicity,ds12$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12$Ethnicity,ds12$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)
```

## HC Comorbidities
```{r HC Comorbidities}
ds12nokid <- filter(ds12, Age>=18)

CrossTable(ds12nokid$Diabetes,ds12nokid$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12nokid$Diabetes,ds12nokid$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

ds12nokid$BMIcat=cut(ds12nokid$BMI,c(0,29.91,100))
CrossTable(ds12nokid$BMIcat,ds12nokid$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12nokid$BMIcat,ds12nokid$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)

# ds12 %>% 
#   group_by(household_infected_at_baseline) %>% 
# summarise(n=sum(!is.na(BMI)))



```
## HC hours per day
```{r}
ds12$`Over.the.past.week,.on.average,.how.many.hours.per.day.have.you.spent.in.the.same.house.with.the.COV-positive.contact?.(not.including.sleeping.hours)`[ds12$`Over.the.past.week,.on.average,.how.many.hours.per.day.have.you.spent.in.the.same.house.with.the.COV-positive.contact?.(not.including.sleeping.hours)`=="No response"]=NA
sum(is.na(ds12$`Over.the.past.week,.on.average,.how.many.hours.per.day.have.you.spent.in.the.same.house.with.the.COV-positive.contact?.(not.including.sleeping.hours)`))
CrossTable(ds12$`Over.the.past.week,.on.average,.how.many.hours.per.day.have.you.spent.in.the.same.house.with.the.COV-positive.contact?.(not.including.sleeping.hours)`,ds12$infected_household,prop.t = F,prop.chisq = F)
```

## HC Education
```{r HC Education}

CrossTable(ds12nokid$`Highest.education.level.(select.one)`,ds12nokid$infected_household,prop.t = F,prop.chisq = F)
CrossTable(ds12nokid$`Highest.education.level.(select.one)`,ds12nokid$household_infected_at_baseline,prop.r = F,prop.t = F, prop.chisq = F)
```


## HC Adjusted P-value
```{r HC adjusted pvalue}
ds12$infectedbi <- factor(ds12$infected_household,levels = 1:2,labels = c("event","noevent"))
ds12$infectedbi <- relevel(ds12$infectedbi,"noevent")

ds12$parentbi=ifelse(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`=="Mother or father (Parent, including in-laws))",1,ifelse(is.na(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`),NA,0))

table(ds12$infectedbi)
m0 <- glmer(infectedbi ~ 1 + (1 | household), data = ds12, family = binomial)
summary(m0)
exp(0.7151)/(1+exp(0.7151))
exp(0.7151)

m1 <- glmer(infectedbi ~ parentbi + (1 | household), data = ds12, family = binomial)
coef(summary(m1))


ds12$childbi=ifelse(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`=="Son or daughter (Child)",1,ifelse(is.na(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`),NA,0))

m2 <- glmer(infectedbi ~ childbi + (1 | household), data = ds12, family = binomial)
coef(summary(m2))
exp(-0.8656+1.96*0.5199)

ds12$partnerbi=ifelse(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`=="Partner",1,ifelse(is.na(ds12$`What.is.your.relationship.to.the.COV-positive.contact.person?.I.am.their`),NA,0))

m3 <- glmer(infectedbi ~ partnerbi + (1 | household), data = ds12, family = binomial)
coef(summary(m3))
exp(1.4085+1.96*0.5979)

m4 <- glmer(infectedbi ~ `Are.you.acting.as.a.primary.caregiver.to.the.COV-positive.person?` + (1 | household), data = ds12, family = binomial)
coef(summary(m4))

ds12$agebi1=ifelse(ds12$Age<18,1,0)
ds12$agebi2=ifelse(18<=ds12$Age&ds12$Age<=50,1,0)
ds12$agebi3=ifelse(ds12$Age>50,1,0)

mage <- glmer(infectedbi ~ agebi3 + (1 | household), data = ds12, family = binomial)
coef(summary(mage))

msex <- glmer(infectedbi ~ Sex + (1 | household), data = ds12, family = binomial)
coef(summary(msex))

names(ds12)[15:27] <- names(ds12)[15:27] %>% 
  substring(regexpr("=",names(ds12)[15:27])+1) %>% 
  str_replace_all(c("\\)"=" ","\\("=" "))
ds12 <- ds12 %>% mutate(Same.bathroom=(ds12$`Same.bedroom.bathroom `=="Checked"|ds12$`Same.general.bathroom `=="Checked"))

ds12$bedroombi=ifelse(ds12$`Same.room.for.sleeping `=="Checked",1,ifelse(is.na(ds12$`Same.room.for.sleeping `),NA,0))

m5 <- glmer(infectedbi ~ bedroombi + (1 | household), data = ds12, family = binomial)
coef(summary(m5))

ds12$bathroombi=ifelse(ds12$Same.bathroom==TRUE,1,ifelse(is.na(ds12$Same.bathroom),NA,0))

m6 <- glmer(infectedbi ~ bathroombi + (1 | household), data = ds12, family = binomial)
coef(summary(m6))

ds12$mealbi=ifelse(ds12$`Meals.eaten.together.at.the.dinner.table `=="Checked",1,ifelse(is.na(ds12$`Meals.eaten.together.at.the.dinner.table `),NA,0))

m7 <- glmer(infectedbi ~ mealbi + (1 | household), data = ds12, family = binomial)
coef(summary(m7))

ds12$carbi=ifelse(ds12$`Shared.car.rides `=="Checked",1,ifelse(is.na(ds12$`Shared.car.rides `),NA,0))

m8 <- glmer(infectedbi ~ carbi + (1 | household), data = ds12, family = binomial)
coef(summary(m8))

m9 <- glmer(infectedbi ~ Mask_at_home + (1 | household), data = ds12, family = binomial)
coef(summary(m9))

ds12$whitebi=ifelse(ds12$Race=="White or Caucasian",1,ifelse(is.na(ds12$Race),NA,0))
ds12$blackbi=ifelse(ds12$Race=="Black or African American",1,ifelse(is.na(ds12$Race),NA,0))
ds12$latinobi=ifelse(ds12$Ethnicity=="Hispanic or Latino",1,ifelse(is.na(ds12$Ethnicity),NA,0))
ds12$otherracebi=ifelse(ds12$Race!="White or Caucasian"&ds12$Race!="Black or African American"&ds12$Race!="Hispanic or Latino",1,0)
table(ds12$whitebi)
m10 <- glmer(infectedbi ~ whitebi + (1 | household), data = ds12, family = binomial)
coef(summary(m10))

m11 <- glmer(infectedbi ~ blackbi + (1 | household), data = ds12, family = binomial)
coef(summary(m11))

m12 <- glmer(infectedbi ~ latinobi + (1 | household), data = ds12, family = binomial)
coef(summary(m12))

mminor <- glmer(infectedbi ~ otherracebi + (1 | household), data = ds12, family = binomial)
coef(summary(mminor))
# mantelhaen.test(xtabs(~parentbi+infected_household+household, data=ds12),alternative = "two.sided",correct = TRUE)
# glimpse(ds12)

# s <- glm(infectedbi~bathroombi,data=ds12,family = binomial)
ds12nokid <- filter(ds12, Age>=18)

datd <- ds12nokid %>% 
  dplyr::select(infectedbi,household,Diabetes) %>% 
  na.omit()

m13 <- glmer(infectedbi ~ Diabetes + (1 | household), data = datd, family = binomial)
coef(summary(m13))

dato <- ds12nokid %>% 
  dplyr::select(infectedbi,household,BMIcat) %>% 
  na.omit()

m14 <- glmer(infectedbi ~ BMIcat + (1 | household), data = dato, family = binomial)
coef(summary(m14))
exp(1.6790+1.96*0.6967)

date <- ds12nokid %>% 
  dplyr::select(infectedbi,household,`Highest.education.level.(select.one)`) %>% 
  na.omit()

date$edubi1 <- ifelse(date$`Highest.education.level.(select.one)`=="High school or lower", 1,0)
m15 <- glmer(infectedbi ~ edubi1 + (1 | household), data = date, family = binomial)
coef(summary(m15))

date$edubi2 <- ifelse(date$`Highest.education.level.(select.one)`=="College degree", 1,0)
m16 <- glmer(infectedbi ~ edubi2 + (1 | household), data = date, family = binomial)
coef(summary(m16))

date$edubi3 <- ifelse(date$`Highest.education.level.(select.one)`=="Graduate degree", 1,0)
m17 <- glmer(infectedbi ~ edubi3 + (1 | household), data = date, family = binomial)
coef(summary(m17))

m <- glmer(infectedbi ~ `Highest.education.level.(select.one)` + (1 | household), data = date, family = binomial)
r <- glmer(infectedbi ~ (1 | household), data = date, family = binomial)
lrtest(m,r)

a <- glm(infectedbi ~ `Highest.education.level.(select.one)`, data = date, family = binomial)
b <- glm(infectedbi ~ 1, data = date, family = binomial)
lrtest(a,b)



```


